### 2020-04-16 serial.tex
caption

\begin{figure}[!th]
\includegraphics[width=\textwidth]{rR.pdf}
\caption{
\textbf{Estimates of the reproduction number from the exponential growth rate.}
}
\label{fig:rR}
\end{figure}

>>>>

\begin{figure}[!th]
\includegraphics[width=\textwidth]{rR.pdf}
\caption{
\textbf{Estimates of the reproduction number from the exponential growth rate based on serial- and generation-interval distributions.}
A. The forward serial-interval distribution during the exponential growth phase give a correct link between the exponential growth rate $r$ and the reproduction number $\mathcal R$.
B. The serial-interval distributions that assume that the backward incubation period of an infector and the forward incubation period of an infectee are identically distributed give an incorrect link between $r$ and $\mathcal R$.
C. The mean forward serial interval during the exponential growth phase depends on $r$.
D. The squared coefficient of variation of forward serial intervals during the exponential growth phase depends on $r$.
}
\label{fig:rR}
\end{figure}
